---
title: Installation
sidebar: false
toc: true
lang: en
---

## Installing `R` and `RStudio`

For this course, you will be using your own computer on which you have [installed or updated](https://pbil.univ-lyon1.fr/CRAN/) `R` (version 4.2.1 for Unix systems and version 4.1.3 for Windows) and the `RStudio` user interface: <https://www.rstudio.com/products/rstudio/>. 

## Installing `brms` and `rstan`

We'll also be using `Stan` via the `brms` and `rstan` packages. You'll find all the info you need to install `brms` on your platform here: <https://learnb4ss.github.io/learnB4SS/articles/install-brms.html>.^[In case of problems, see also: <https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started>.]

Please note that this step can be quite long and complex, depending on your platform (especially on Windows), so make sure you don't do it at the last minute, and that everything's up and running at the start of the course.

## Installing `imsb`

The rest of the packages, along with the data used in the exercises and a few useful functions, can be installed together as a "companion" package to the training, the `imsb` package. To install it, you first need to install the `remotes` package (and `tidyverse` by the way), then install `imsb` from Github.^[Yeah, the `imsb` acronym comes from the French name of the course I am teaching, hence the loose correspondence with this course's acronym.]

```{r, eval = FALSE, echo = TRUE}
install.packages(pkgs = c("remotes", "tidyverse") )
options(timeout = 240) # allowing more time to download the package
remotes::install_github(repo = "lnalborczyk/IMSB2022/_imsb", dependencies = TRUE)
```

During the course, this package can be used to read the slides of the various courses (from course `01` to course `04`) online via the `open_slides()` function.

```{r, eval = FALSE, echo = TRUE}
library(imsb)
open_slides(01)
```

The datasets used in the various exercises are also contained in this package. You can import them using the function `open_data()`.

```{r, eval = FALSE, echo = TRUE}
open_data(robot)
```

## Reminder regarding the pre-requisites

Although a good knowledge of `R` is a **pre-requisite for registration**, you will find [here](https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf) a short introduction to the basics of the language, which will be necessary to fully understand the examples covered during the course.
