---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "50%"
  )
```

# IMSB: Introduction à la modélisation statistique bayésienne

<!-- badges: start -->
`r badger::badge_custom("version", badger::ver_devel(), color = "FFA70B")`
[![GitHub last commit](https://img.shields.io/github/last-commit/lnalborczyk/IMSB2022?color=orange&logo=github)](https://github.com/lnalborczyk/IMSB2022)
<!-- badges: end -->

The goal of the `imsb` package is to provide all the materials (e.g., data, utility functions) needed for the [IMSB course](https://www.barelysignificant.com/IMSB2022/).

## Installation

You can install the development version of `imsb` from GitHub with:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github(repo = "lnalborczyk/IMSB2022/_imsb", dependencies = TRUE)
```

## Usage

Checking the `brms` and `rstan` install.

```{r loading, eval = TRUE, echo = FALSE}
library(imsb)
```

```{r example1, eval = FALSE}
library(imsb)
check_install()
```

Opening the slides of the first course in browser.

```{r example2, eval = FALSE}
open_slides(cours = 01)
```

Importing the `robot` data.

```{r example3, eval = FALSE}
open_data(robot)
```

Posterior plot in the style of the `BEST` package using the `imsb::posterior_plot()` function.

```{r example4, eval = TRUE, dev = "png", dpi = 300}
# getting samples for a normal distribution
samples <- rnorm(n = 1e3, mean = 0, sd = 1)

# plotting it
posterior_plot(samples, credmass = 0.96, compval = 1) +
    # the resulting plot is a ggplot than can be customised at will
    ggplot2::labs(x = expression(theta) )
```
